\documentclass[A4]{report}


\title{The NSSF Yellow Fever Screening and Treatment Initiative}
\author{By Kyobweine Bikangaga Prisca
\\
216002579
\\
16/U/6489/PS}
\begin{document}
\maketitle
Yellow fever is a deadly disease caused by a virus (Flavivirus) which is transmitted to humans by the bites of infected aedes and haemogogus mosquitoes. Yellow fever virus is mainly found in tropical and subtropical areas in South America and Africa. Mild cases cause fever, headache, nausea and vomiting while serious cases may cause fatal heart attacks, liver and kidney conditions.\\
No specific treatment for the disease exists. Efforts focus on managing symptoms and limiting complications.
\\
\\
The National Social Security Fund(NSSF) has come up with a vaccination initiative that will run for a week in numerous medical camps/hospitals, in which patients are to be screened for yellow fever and if found negative, they are vaccinated against the disease and given the appropriate medical attention if found positive.\\
The initiative is open to any citizen of the country who has not been vaccinated yet and it is completely free of charge.\\The different medical camps will run vaccination exercises from 9.00am till 4.00pm.\\
People are encouraged to come, as proof of yellow fever vaccination is a necessity when leaving the country.
\\
\\
A medical form that requires the details about the patient such as their name, age and even a passport size photo is to be filled.\\The form is filled in by the medical personnel to prevent falsified data in the system. The entered data is the automatically entered into a database.
\\
\\
The purpose of using the form is to organise the data so that in case of any need to check for the medical records of a patient, even from a different medical camp, one can easily find the required medical record just by using the patient's name or in case of more than one patient having the same name, the patientID is then used to identify exact which patient's record is needed.
 
\end{document}          
